D3064R0: How to Avoid OOTA Without Really Trying

### 2024-03-10 ootavacuous.tex
Move simple-reordering litmus test to Section 1.3
Signed-off-by: Paul E. McKenney <paulmck@kernel.org>

The earlier examples shown in
Listings~\ref{lst:Simple OOTA}
and~\ref{lst:Simple Reordering}
can be recast as similar \co{herd7} litmus tests, as shown in
Listing~\ref{lst:Causality Test Case 4}
on page~\pageref{lst:Causality Test Case 4}
and Listing~\ref{lst:Simple Reordering as Litmus Test}
on page~\pageref{lst:Simple Reordering as Litmus Test}, respectively.
Other OOTA-related litmus tests may be found in
Appendix~\ref{app:Illustrative Litmus Tests}
and
Appendix~\ref{app:Litmus Tests from “Causality Test Cases"}.

@@

% \subsection{Simple Reordering as Litmus Test}
% \label{app:Simple Reordering as Litmus Test}

% Listing~\ref{lst:Simple Reordering as Litmus Test}
% shows how
% Listing~\ref{lst:Simple Reordering}
% can be recast into a \co{herd7} litmus test.

>>>>

Later examples will usually combine the litmus test and the \co{herd7}
output into one listing, as shown in
Listing~\ref{lst:Simple Reordering as Litmus Test},
which recasts
Listing~\ref{lst:Simple Reordering}
into litmus-test form.
Listing~\ref{lst:Simple OOTA}
can be also recast as a \co{herd7} litmus test, as shown in
Listing~\ref{lst:Causality Test Case 4}
on page~\pageref{lst:Causality Test Case 4}.
Other OOTA-related litmus tests may be found in
Appendix~\ref{app:Illustrative Litmus Tests}
and
Appendix~\ref{app:Litmus Tests from “Causality Test Cases"}.

@@
